Efficient pedigree recording for fast population genetics simulation

### 2017-11-17 forwards_paper.tex
reorg idea for API overview

The tables API is primarily designed to facilitate efficient interchange of
data between programs or between different modules of the same program.
Following the current best-practises [citations: apache arrow, etc] data is stored
in a columnar format.
The principal advantage of this for our purposes is that it allows for very efficient
interchange of large amounts of numerical data. In principle, this enables
zero-copy semantics, where a data consumer can read the information directly
from the memory of a producer without incurring the overhead of a copy
[citation?] Our implementation uses the numpy C API [citation] to efficiently copy
data from Python into the low-level C library used to manipulate
tree sequences.

@@

\plr{Maybe we don't need this paragraph? Already said it, more or less, above, esp if we insert something about how fwdpp works.}
This interchange API is very efficient. [Describe a quick example where we generate
a many-gigabyte tree sequence using fwdpp, and the time required
to copy the node and edge data into the tables]. By using a simple numerical
encoding of tree topologies and contiguous arrays of data to store this
encoding, we can achieve data transfer rates that would be impossible under
any text-based approach while retaining excellent portability.

>>>>

The tables API is primarily designed to facilitate efficient interchange of
data between programs or between different modules of the same program.
Following the current best-practises [citations: apache arrow, etc] data is stored
in a columnar format.
The principal advantage of this for our purposes is that it allows for very efficient
interchange of large amounts of numerical data. In principle, this enables
zero-copy semantics, where a data consumer can read the information directly
from the memory of a producer without incurring the overhead of a copy
[citation?] Our implementation uses the numpy C API [citation] to efficiently copy
data from Python into the low-level C library used to manipulate
tree sequences.
Thus, by using a simple numerical
encoding of tree topologies and contiguous arrays of data to store this
encoding, we can achieve data transfer rates that would be impossible under
any text-based approach while retaining excellent portability.

@@

\plr{Maybe we don't need this paragraph? Already said it, more or less, above, esp if we insert something about how fwdpp works.}
\jda{agree re the next two lines. propose moving the other above}
This interchange API is very efficient. [Describe a quick example where we generate
a many-gigabyte tree sequence using fwdpp, and the time required
to copy the node and edge data into the tables].
